\LARGE\bf Adapting the Chumbley Score to match striae on Land Engraved Areas (LEAs) of bullets

### 2018-06-29 jfs_submission/paper-main-manuscript.tex
jfs_submission.

\usepackage{url} % not crucial - just used below for the URL

@@

\if0\blind
{
  \title{\bf Adapting the Chumbley Score to match striae on Land Engraved Areas of
bullets}

  \author{
        Ganesh Krishnan,\\ %\\
    Master of Science (M.Sc.)\\
    % \\
     and \\     Prof.~Heike Hofmann,\\ %\\
    Doctor of Philosophy (Ph.D.)\\
    % \\
      }
    \maketitle
  \bigskip
  \begin{center}
  {\textbf{Affiliation(s)}\\
  Department of Statistics, Iowa State University and CSAFE (Center for
  Statistics and Applications in Forensic Evidence)\\
  \bigskip
  \textbf{Source of funding}\\
  The authors gratefully acknowledge funding from CSAFE through
  cooperative agreement \# 70NANB15H176 between NIST and Iowa State
  University.\\
  \bigskip
  \textbf{Acknowledgement}\\
  We would like to thank the efforts of CSAFE and Roy J Carver Microscopy
  lab in scanning the Hamby-44 set and providing the scans to us. We would
  also like to thank NIST for providing the Hamby-44 bullets to us for
  scanning.\\
  \bigskip
  \textbf{Information on presentation of work}\\
  This work was presented in the form of a poster in the AFTE 2018 49th
  Annual Training Seminar, held from June 3rd to June 8th, 2018 in
  Charleston, West Virginia}
  \end{center}

} \fi

  % \bigskip

  % \bigskip
\newpage

\if0\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
  \title{\LARGE\bf Adapting the Chumbley Score to match striae on Land Engraved Areas of
bullets}
  \end{center}
  \bigskip
  \maketitle
} \fi

% \if1\blind
% {
%   \bigskip
%   \bigskip
%   \bigskip
%   \begin{center}
%     {\LARGE\bf Adapting the Chumbley Score to match striae on Land Engraved Areas of
bullets}
%   \end{center}
%   \medskip
% } \fi

@@

i.e.~for an odd number of same-shift correlations, we skip the middle
pair for the different-shift correlations (see \autoref{sketch-diff-2}).
This pairing ensures that the number of different-shift pairings is the
same or at most one less than the number of same-shift pairings in all
tests. In the remainder of the paper, we will refer to the algorithm
defined by \citet{hadler} as \textbf{(CS1)} and the suggested modified
algorithm as \textbf{(CS2)} and compare their performance on the
available scans of the Hamby study. The section
\ref{appendix:appxfailed} of the Appendix discusses about the various
scenarious of failed tests.

@@

The results from Figures \ref{fig:roc} and \ref{fig:eer} are summarized
in numbers in \autoref{tab:aucs}. Equal error rates (EER), rates for
false positives (FPR) and false negatives (FNR) are shown side by side
with the area under the curve (AUR) for both methods for a set of
different optimization windows \(w_o\) and a validation window \(w_v\)
of 30 pixels. The rate of false positive same-source identifications is
equal to the statistical type I error rate, which is set to
\(\alpha = 0.05\) for this example. The rate of false negatives are
missed same-source markings. This rate is also known as the type II
error rate. A detailed plot on the type II error rates for CS1 and CS2
can be found in the section \ref{appendix:appxtype2} of the Appendix.
Area under the curve (AUC) is shown with confidence intervals as given
by \citet{delong}. CS2 significantly outperforms CS1 with respect to its
predictive power in most situations.

@@

\section{Appendix}\label{appendix}

@@

\subsection{Scenarios of failed tests}
\label{appendix:appxfailed}
Figures \ref{same-shift-failure} and \ref{diff-shift-failure} show scenarios in which the deterministic Chumbley score can fail. 
In \autoref{same-shift-failure} both CS1 and CS2 fail, because the lag between optimal locations is so large that no same-shift pairs can be found once the signatures are aligned. These failures are inherent to the Chumbley Score and cannot be prevented.
\begin{figure}[hbtp]
\centering
\includegraphics[width=0.62\textwidth]{images/same-shift-failure.png}

@@

\newpage
\subsection{Type 2 errors: CS1 vs CS2}
\label{appendix:appxtype2}
\autoref{fig:type2} gives an overview of type 2 error rates of methods CS1 and CS2 for different significance levels $\alpha$. Method CS2 is outperforming CS1 significantly in every instance.

@@

\end{appendix}

\bibliographystyle{agsm}
\bibliography{bibliography}

>>>>

\usepackage{verbatim}
\usepackage{url} % not crucial - just used below for the URL

@@

\if0\blind
{
  \title{\LARGE\bf Adapting the Chumbley Score to match striae on Land Engraved Areas (LEAs) of bullets}
  \maketitle
} \fi

% \if1\blind
% {
%   \bigskip
%   \bigskip
%   \bigskip
%   \begin{center}
%     {\LARGE\bf Adapting the Chumbley Score to match striae on Land Engraved Areas}
%   \end{center}
%   \medskip
% } \fi

@@

i.e.~for an odd number of same-shift correlations, we skip the middle
pair for the different-shift correlations (see \autoref{sketch-diff-2}).
This pairing ensures that the number of different-shift pairings is the
same or at most one less than the number of same-shift pairings in all
tests. In the remainder of the paper, we will refer to the algorithm
defined by \citet{hadler} as \textbf{(CS1)} and the suggested modified
algorithm as \textbf{(CS2)} and compare their performance on the
available scans of the Hamby study. The section  A %\ref{appendix:appxfailed} 
of the Appendix discusses about the various scenarious of failed tests.

@@

The results from Figures \ref{fig:roc} and \ref{fig:eer} are summarized
in numbers in \autoref{tab:aucs}. Equal error rates (EER), rates for
false positives (FPR) and false negatives (FNR) are shown side by side
with the area under the curve (AUR) for both methods for a set of
different optimization windows \(w_o\) and a validation window \(w_v\)
of 30 pixels. The rate of false positive same-source identifications is
equal to the statistical type I error rate, which is set to
\(\alpha = 0.05\) for this example. The rate of false negatives are
missed same-source markings. This rate is also known as the type II
error rate. A detailed plot on the type II error rates for CS1 and CS2 
can be found in the section B %\ref{appendix:appxtype2} 
of the Appendix.\\
Area under the curve (AUC) is shown with confidence intervals as given
by \citet{delong}. CS2 significantly outperforms CS1 with respect to its
predictive power in most situations.

@@

\begin{comment}
\section{Appendix}\label{appendix}

@@

\section{Scenarios of failed tests}
\label{appendix:appxfailed}
Figures \ref{same-shift-failure} and \ref{diff-shift-failure} show scenarios in which the deterministic Chumbley score can fail. 
In \autoref{same-shift-failure} both CS1 and CS2 fail, because the lag between optimal locations is so large that no same-shift pairs can be found once the signatures are aligned. These failures are inherent to the Chumbley Score and cannot be prevented.
\begin{figure}[hbtp]
\centering
\includegraphics[width=0.62\textwidth]{images/same-shift-failure.png}

@@

\newpage
\section{Type 2 errors: CS1 vs CS2}
\label{appendix:appxtype2}
\autoref{fig:type2} gives an overview of type 2 error rates of methods CS1 and CS2 for different significance levels $\alpha$. Method CS2 is outperforming CS1 significantly in every instance.

@@

\end{appendix}
\end{comment}
\newpage
\bibliographystyle{agsm}
\bibliography{bibliography}
